Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-19 journal paper/itcs18paper/app-examples.tex
Minor edits.
fix missing space
small comment on ts
small comment

This appendix provides some auxiliary results on \bmonotonicity of some standard algorithms: \DynGreedy, \DynamicEpsGreedy and \Thompson. The former is needed in Section~\ref{sec:theory}, the last two merely add motivation for our theoretical story. The result on\Thompson also implies that $\BIR(t)\leq \tildeO(t^{-1/2})$. Recall that an algorithm is called \bmonotone if its Bayesian-expected reward is non-decreasing in time.

We consider a simple setting of Bayesian MAB with Bernoulli rewards. There are $T$ rounds and $K$ arms. In each round $t\in [T]$, the algorithm chooses an arm $a_t\in A$ and receives a reward $r_t\in\{0,1\}$ for this arm, drawn from a fixed but unknown distribution. The set of all arms is $A$; mean reward of arm $a$ is denoted $\mu_a$. \asedit{The mean reward vector $\mu = (\mu_a:\; a\in A)$ is drawn from a common Bayesian prior $\priorMu$.}
We let
    $\rew(t) = \mu_{a_t}$
denote the instantaneous mean reward of the algorithm.

@@

The theorem follows easily from two observations in  \citet{Selke-BE-2020}, we provide the proof for completeness. First, let us state the algorithm. Let $\Pr^t$ and $\E^t$ denote, resp., Bayesian posterior probability and expectation conditional on the history observed at time $t$. Let $a^*$ be the best arm: $a^*\in \argmax_a \mu_a$. In each round $t$, \Thompson samples arm $a_t$ as follows:
\begin{align}\label{eq:TS-defn}
    \Pr[a_t=a] := {\Pr}^t[a^*=a]
    \quad\text{for each arm $a$}.
\end{align}

@@

>>>>

This appendix provides some auxiliary results on \bmonotonicity of some standard algorithms: \DynGreedy, \DynamicEpsGreedy and \Thompson. The former is needed in Section~\ref{sec:theory}, the last two merely add motivation for our theoretical story. The result on \Thompson also implies that $\BIR(t)\leq \tildeO(t^{-1/2})$. Recall that an algorithm is called \bmonotone if its Bayesian-expected reward is non-decreasing in time.

We consider Bayesian MAB with Bernoulli rewards. There are $T$ rounds and $K$ arms. In each round $t\in [T]$, the algorithm chooses an arm $a_t\in A$ and receives a reward $r_t\in\{0,1\}$ for this arm, drawn from a fixed but unknown distribution. The set of all arms is $A$; mean reward of arm $a$ is denoted $\mu_a$. \asedit{The mean reward vector $\mu = (\mu_a:\; a\in A)$ is drawn from a common Bayesian prior $\priorMu$.}
We let
    $\rew(t) = \mu_{a_t}$
denote the instantaneous mean reward of the algorithm.

@@

The theorem follows easily from two observations in  \citet{Selke-BE-2020}, we provide the proof for completeness. First, let us state the algorithm. Let $\Pr^t$ and $\E^t$ denote, resp., Bayesian posterior probability and expectation conditional on the history observed at time $t$. Let $a^*$ be the best arm: $a^*\in \argmax_a \mu_a$. In each round $t$, \Thompson samples arm $a_t$ as follows:
\begin{align}\label{eq:TS-defn}
    \Pr[a_t=a] := {\Pr}^t[a^*=a]
    \quad\text{for each arm $a$}.
\end{align}
\swcomment{do we want to say $\Pr$ is over sampling first from prior and then generate history?}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../journal_main"
%%% End:
